---
title: "Building Research Leaders for Early Career Researchers"
subtitle: "Evaluation (December 2025)"
# author: "Jen Beaudry"
# date: "2025-10-12"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{caption}
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=0.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \fancyfoot[L]{Building Research Leaders for ECRs} # my name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE, 
                      eval = TRUE)

```


```{r library, include=FALSE}

# devtools::install_github("adletaw/captioner")

library(here)
library(tidyverse)
library(kableExtra)
library(RColorBrewer)
library(captioner)

```

```{r run preprocessing script, include = FALSE}

source(here("analysis", "brl_preprocessing.R"))

```


```{r functions, include = FALSE}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position", "repeat_header"))
}

source(here("..", "functions", "meta_rename.R"))
source(here("..", "functions", "ratings_summary.R"))

table_nums <- captioner(prefix = "Table")
fig_nums <- captioner(prefix = "Figure")

```


```{r captions, include = FALSE}

# I'm using this to allow me to reference the tables. 
# I'm using kable for the captions within the tables because it allows me to break 
  # the table over the pages

table_nums(name = "info_workshop", 
           caption = "'What did you expect from this workshop?'")

table_nums(name = "expectations", 
           caption = "'Please elaborate on how the workshop aligned with your expectations.'")

table_nums(name = "career_stage", 
           caption = "'Please elaborate on whether this workshop was appropriate for your career stage.'")

table_nums(name = "action", 
          caption = "'Did this workshop inspire you to take any immediate action(s)?'")

table_nums(name = "success",
             caption = "'Do you credit any research successes to the workshop?'")

table_nums(name = "best_parts",
             caption = "'What were the best parts of the workshop?'")

table_nums(name = "improvement",
             caption = "'Any suggestions for improvement?'")

table_nums(name = "anything_else",
             caption = "'Anything else you want us to know?'")

table_nums(name = "attendance", 
           caption = "We asked participants to explain why they attended the number of sessions that they did.")

fig_nums(name = "ratings_summary", 
         caption = "Ratings of different aspects of the workshop")

```



```{r load data, include=FALSE}

df <- read_csv(here::here("data", "brl_eval_processed_data.csv"), lazy = FALSE)

```


```{r code factors, include=FALSE}


# turn all ratings variables into factors, use datapasta to do this!
# the code below works

df$expectations <- factor(
  df$expectations,
  levels = c(
    "Exceeded my expectations",
    "Met my expectations",
    "Partly met my expectations",
    "Did not meet my expectations"
  )
)


df$post_phd <- factor(
  df$post_phd,
  levels = c(
    "Less than 5 years post-PhD",
    "5 to 10 years post-PhD",
    "11 to 15 years post-PhD"
  )
)
#   "More than 15 years post-PhD" [no one]

# work with all rating items together because they have the same levels

cols <- c("research_leadership",
  "research_productivity",
  "expert",
  "engaging",
  "balance",
  "current_role",
  "future_roles",
  "reengagement")


# turn the cols columns into factors
df <- df %>% 
  mutate(across (all_of(cols), ~factor(., 
                                       levels = c("N/A", 
                                           "Strongly disagree",
                                           "Somewhat disagree",
                                           "Neither agree nor disagree",
                                           "Somewhat agree",
                                           "Strongly agree"))))

```


```{r sessions attendance}

participants <- 18

#breadcrumb for caption: \captionsetup[table]{labelformat=empty}
# that's if I include header use caption in the yaml

```


# Executive Summary

This report provides the feedback from the 2025 
*Building Research Leaders for Early Career Researchers* workshop series offered to 
`r participants` early career researchers (ECRs) at Flinders University. This workshop
series was sponsored by the Deputy Vice-Chancellor (Research) and participants 
were nominated by the College Deans (Research). 

The majority of the respondents found the workshop series valuable, engaging, 
and informative. They also appreciated the opportunity to connect with other ECRs 
across the University. Importantly, they reported that the workshop series inspired 
them to take immediate actions including finishing manuscripts that were near submission 
and scheduling time for research. They also attributed several successes to the 
workshop series, including new publications and a renewed commitment to focusing
more on their core work. 

As indicated in my 2024 report, the workshop series does little to address 
research leadership, but it does help the ECRs to develop the skills they need to 
be a successful researcher, particularly for those balancing research with teaching or clinical roles,
in the current academic environment. 

I recommend running this program again, targeting recruitment at early career 
researchers who are not in research-only roles. I also recommend revising the 
title to something more appropriate like "Thriving in Research for Early Career 
Researchers" or "Research Productivity Skills for Early Career Researchers". 


# Detailed Evaluation

Hugh Kearns from ThinkWell designed and delivered the 
*Building Research Leaders for Early Career Researchers* workshop. This workshop 
was run as series of three full-day sessions from April to October 2025. 
Of the `r participants` participants in the workshop, `r nrow(df)` completed this evaluation.

In previous years, this series was offered over 6 days (one full day and five half-days). 
In response to less than ideal attendance, I requested that Hugh collapse
the material into fewer full days, with the hopes that attendance would be better. 
Psychologically, it's easier to commit to three full days rather than 
five half-days. We started this approach in 20214, and it worked well 
again in 2025; our attendance rate of 91% across the three days confirmed that 
this format worked for our participants. 

On average, the respondents to this survey attended `r round(mean(df$attendance),2)` 
of the 3 sessions, with everyone attending at least `r min(df$attendance)` sessions.
Their explanations for why they attended the number of sessions that they did are shown in 
`r table_nums("attendance", display = "cite")` in the Appendix. Most respondents indicated
that they attended all three sessions because they valued the development opportunity; 
the two who reported that they could not attend one session cited a medical appointment
and "competing demands". In response to another question, one researcher reported 
that three full-day sessions worked well because they "could block out that time and prioritise it" 
(see `r table_nums("improvement", display = "cite")`).

We asked participants to rate several items about the workshop and the trainer 
on a scale from 'strongly disagree' to 'strongly agree' (see 
`r fig_nums(name = "ratings_summary", display = "cite")`). Most respondents
agreed with the statements, with only a few neutral ratings and no disagreement ratings. 
Importantly, all respondents agreed that Hugh was engaging, an expert in the sector, 
that the  content would be useful in their future roles, and that they learned 
strategies to increase their research productivity.

\
`r fig_nums(name = "ratings_summary")`

```{r creating tibbles for all ratings, include = FALSE}

# get total n to calculate percentages

total_n <- length(df$id)

# SELECT THE RATING COLUMNS & SAVE AS A TIBBLE I WANT TO SUMMARISE & PLOT USING THE RATING_SUMMARY FUNCTION

ratings <- df %>% 
  select (c("research_leadership",
  "research_productivity",
  "expert",
  "engaging",
  "balance",
  "current_role",
  "future_roles",
  "reengagement"))

# UPDATE THE COLUMNS PARAMETER WITH THE STRINGS FROM ABOVE

columns <- c("research_leadership",
  "research_productivity",
  "expert",
  "engaging",
  "balance",
  "current_role",
  "future_roles",
  "reengagement")

# RUN THE FUNCTION & APPLY TO ALL COLUMNS IN OUR DF

ratings_summary <- purrr::map_dfr(columns, .f = function(column) {
	ratings_summary(ratings, column)
})

# remove the NA responses
ratings_summary <- na.omit(ratings_summary)


# also, figure out how many responded with the agree ratings. I use these in the 
  # text summaries later

# [breadcrumb: can I use apply for this too?? need to do this later!]

agree <- c("Strongly agree", "Somewhat agree")


```

```{r plot the ratings}

# Relevel the responses [changes order in ggplot, but not the dataframe]
# plot it first to see if I need to do this

# tor_rating$rating <- factor (rating$rating, levels = c("Strongly agree",
#                                            "Somewhat agree",
#                                            "Neither agree nor disagree",
#                                            "Somewhat disagree",
#                                            "Strongly disagree"))

# put them in reverse order of how I want them to appear
ratings_summary$rating_item <-
  factor (
    ratings_summary$rating_item,
    levels = c(
      "reengagement", 
      "future_roles",
      "current_role",
      "balance",
      "engaging",
      "expert",
      "research_leadership",
      "research_productivity"
    )
  )

# [breadcrumb] I can delete this later, but this is useful to create the plot_labs

# labs <- meta %>%
#   filter(scale == "common_ratings") %>%
#   pull(item_text_short) %>%
# datapasta::vector_paste_vertical()


# plot it


ggplot(ratings_summary, aes(fill = rating, y = percentage, x = rating_item)) +
  geom_bar(position="fill", stat="identity", colour = "black") +
  scale_fill_brewer(
    palette = "Blues",
    na.value = "grey50",
    direction = 1,
    labels = c(
      "N/A",
      "Strongly disagree",
      "Somewhat disagree",
      "Neither agree nor disagree",
      "Somewhat agree",
      "Strongly agree"
    )
  ) +
  labs (x = element_blank(),
        y = "Percentage") +
  theme_classic() +
theme(legend.title = element_blank()) +
    coord_flip() +
  scale_x_discrete(
    labels = c(
      "I would attend another \nworkshop from this trainer",
      "I expect that the content will be \nuseful in my future role(s)",
      "The workshop content was relevant \nto my current role",
      "The workshop had a good balance \nof group discussion and presentation",
      "The trainer was very engaging",
      "The trainer is an expert \nin the sector",
      "The workshop provided me with \na greater understanding of \nresearch leadership",
      "The workshop provided me with \nstrategies to increase my \nresearch productivity"
 )
) +
  scale_y_continuous(labels = c("0", "25", "50", "75", "100"))

# FYI: the labels are always in opposite directions from the data set!

```

\

As indicated in `r table_nums("info_workshop", display = "cite")`, the respondents
had several expectations of the workshop series, including learning about research
leadership, tips to thrive as a balanced academic, building a research profile, 
and general career advice for those early in their academic career. 


```{r info_workshop table, include = TRUE}

info_workshop <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, info_workshop) %>% 
  filter (!is.na(info_workshop))


kable(
  info_workshop,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'What did you expect from this workshop?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  styler_pdf

```


```{r expectations data, include = TRUE}

expect <- df %>% 
    dplyr::group_by (expectations) %>% 
  count()

```


The respondents varied as to whether the program met their expectations. Of the `r sum(expect$n)` respondents,  

  * `r round((expect[1,2]/nrow(df))*100,2)`% (*n* = `r expect[1,2]`) said that the program exceeded their expectations,
  * `r round((expect[2,2]/nrow(df))*100,2)`% (*n* = `r expect[2,2]`) said that the program met their expectations, and
  * `r round((expect[3,2]/nrow(df))*100,2)`% (*n* = `r expect[3,2]`) said that the program partly met their expectations. 
  * No one said that the program did not meet their expectations. 

Their explanations of how the program aligned with their expectations are shown 
in `r table_nums("expectations", display = "cite")`. As mentioned in the Executive 
Summary, most of the responses were very positive about the program. One researcher, 
however, felt that the content was targeted more toward PhD students; in contrast,
other researchers indicated that the workshops focused on excelling in research
as academics.

```{r expectations table, include = TRUE}

expectations <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, expect_comment) %>% 
  filter (!is.na(expect_comment))


kable(
  expectations,
  format = "latex",
  longtable = T,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Please elaborate on how the workshop aligned with your expectations.'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  styler_pdf

```


```{r career stage, include = TRUE}

# remove the post-PhD because it's repeated in every response
df$post_phd <- str_remove(df$post_phd, " post-PhD")


years <- df %>% 
    dplyr::group_by (post_phd) %>% 
  count()

# change the text to be used in the markdown
years$post_phd <- str_replace(years$post_phd, "Less", "less")


```


We had a mix of participants in this workshop (nominated by their Deans of Research). 
The respondents to the survey reflected this mix; `r years[2,2]` respondents
were `r years [2,1]` post-PhD and `r years[1,2]` respondents were `r years [1,1]` post-PhD. 

Participants reported whether or not the program aligned with their career 
stage and explained why or why not it was suited to them (see `r table_nums("career_stage", display = "cite")`).
These responses were interesting because with the exception of one of the 
more junior researchers, all respondents thought it was appropriate for their career
stage regardless of whether their PhD was conferred more or less than 5 years ago.


```{r careerstage table, include = TRUE}

career_stage <- df %>% 
  select(c(id, post_phd, careerstage_yes, careerstage_no)) %>% 
  replace_na(list(careerstage_yes = "", careerstage_no = "")) %>% 
  arrange(desc(post_phd))


kable(
  career_stage,
  format = "latex",
  booktabs = T, 
  align = c('clll'),
  linesep = "\\addlinespace",
  caption = "'Please elaborate on whether this workshop was appropriate for your career stage.'",
  col.names = c("Respondent", "Years post PhD", "Reasons why it was appropriate", "Reasons why it was not appropriate")
  ) %>%
  column_spec (column = 3, width = "5cm") %>%
   column_spec (column = 4, width = "5cm") %>%
  styler_pdf

```

As shown in `r table_nums("action", display = "cite")`, respondents were inspired
by the program to take a variety of actions ranging from developing and revising 
research plans, implementing strategies for paper writing, tackling 'zombie' 
manuscripts that were near submission, better time management, and seeking out new collaborations.

```{r action table, include = TRUE}

action <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, actions) %>% 
  filter (!is.na(actions))


kable(
  action,
  format = "latex",
  longtable = T,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Did this workshop inspire you to take any immediate action(s)?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  styler_pdf

```

As shown in `r table_nums("success", display = "cite")`, some but not all respondents 
credited research successes to the workshop series, including publications, successful 
grant applications and new research collaborations. 


```{r success table, include = TRUE}

success <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, success) %>% 
  filter (!is.na(success))


kable(
  success,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Do you credit any research successes to the workshop?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  styler_pdf

```


The best parts of the workshop included interacting with other colleagues across 
the University, having an opportunity to plan for their careers, and realising
that everyone is facing the same hurdles (see `r table_nums("best_parts", display = "cite")`).


```{r best_parts table, include = TRUE}

best <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, best_parts) %>% 
  filter (!is.na(best_parts))

kable(
  best,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'What were the best parts of the workshop?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  styler_pdf

```

Participants had a few suggestions as to how the program could be improved, 
including focusing more on leading grant-funded projects and focusing more on 
all three roles of an academic rather than solely on research 
(see `r table_nums("improvement", display = "cite")`). I will inform Hugh that 
the respondents would prefer less time hearing from their colleagues. Although this 
is an important part of the workshop series, it seems that the focus needs to 
swing back to allow a little less time for sharing. 

```{r improvement table, include = TRUE}

improve <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, improvement) %>% 
  filter (!is.na(improvement))


kable(
  improve,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Any suggestions for improvement?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  styler_pdf

```


Finally, we asked the participants if there was anything else they wanted us to know
(see `r table_nums("anything_else", display = "cite")`).


```{r anything else table, include = TRUE}

anything_else <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, anything_else) %>% 
  filter (!is.na(anything_else))


kable(
  anything_else,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Anything else you want us to know?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  styler_pdf


```

\


If you have any questions about this workshop series or report, please contact 
Dr Jen Beaudry, Manager, Researcher Training, Development and Communication in 
Research Development and Support. 

\newpage
# Appendix

```{r attendance table, include = TRUE}


attendance <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, attendance_text) %>% 
  filter (!is.na(attendance_text))


kable(
  attendance,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "We asked participants to explain why they attended the number of sessions that they did.",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  styler_pdf



```


